Appendix

### 2023-07-23 manuscript/_appendix/_model-doe.qmd
Fix bug in appendix

tbl_data |> 
    mutate(viz = "") |> 
    select(-c(.lower, .upper)) |> 
    knitr::kable(
        format = "latex", 
        escape = FALSE,
        col.names = c("",
                      "$\\beta$",
                      "95\\% HDI",
                      "$p(\\text{ROPE})$",
                      ""),
        digits = 3,
        booktabs = TRUE,
        align = "lclr",
        linesep = ""
    ) |> 
    kableExtra::pack_rows("Model: Exposure",
                          start_row = 1,
                          end_row = 8) |> 
    kableExtra::pack_rows("Model: Frequency & DoE",
                          start_row = 9,
                          end_row = 17)
```

>>>>

tbl_data |> 
    select(-c(.lower, .upper)) |> 
    knitr::kable(
        format = "latex", 
        escape = FALSE,
        col.names = c("",
                      "$\\beta$",
                      "95\\% HDI",
                      "$p(\\text{ROPE})$"),
        digits = 3,
        booktabs = TRUE,
        align = "lclr",
        linesep = ""
    ) |> 
    kableExtra::pack_rows("Model: Exposure",
                          start_row = 1,
                          end_row = 8) |> 
    kableExtra::pack_rows("Model: Frequency & DoE",
                          start_row = 9,
                          end_row = 17)
```

### 2023-07-23 manuscript/appendix.qmd
Fix bug in appendix

format:
  arxiv-pdf:
    keep-tex: true  
    linenumbers: true
    doublespacing: false
    runninghead: "Cognate beginnings to bilingual lexical acquistion (Appendix)"
    include-in-header: 
      text: |
        \usepackage{tipa}
        \usepackage{booktabs}
---

>>>>

format:
  arxiv-pdf:
    linenumbers: true
    doublespacing: false
    runninghead: "Cognate beginnings to bilingual lexical acquistion (Appendix)"
    include-in-header: 
      text: |
        \usepackage{tipa}
        \usepackage{booktabs}
---
